Global Assessments of Fishery Status need Better Data more than Better Models

### 2020-08-06 documents/ovando-etal-assessing-global-fisheries.Rmd
merging back to master

---
title: "Global Assessments of Fishery Status need Better Data more than Better Models"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::pdf_document2: default
params:
  results_name: ["v0.5"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, formulating evidence-based policy and tracking the implementation of the United Nations Sustainable Development Goals. Numerous high-profile publications featuring a range of statistical methods have produced estimates of the global status of fisheries, but limited quantity and quality of data along with methdological differences have produced counterintuitive and conflicting results and therefore, high uncertainties in our understanding of global fisheries. This is especially true in areas such as Southeast Asia and Africa which are also regions that have high dependence on fishery resources. How can we effectively estimate the state of global fishery sustainability and track progress towards the Sustainable Development Goals targets? We developed a new flexible assessment model to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion through Fisheries Management Index scores, and increasingly available but historically underutilized data such as trawl footprints and effort data. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world, and to identify priority data types for future collection. We show that our ability to obtain reliable estimates of stock status for the world's unassessed fisheries depends on prioritizing the collection of key data at a global scale, not on the development of new modeling methods alone.
always_allow_html: true
---

@@

<!-- <!-- Evaluating the validity of data-limited assessments methods can be challenging. Simulation testing provides one avenue, but it can be difficult to create a simulation environment that adequately captures the problems of real-world ecosystems and data. We can also compare results between data-limited assessment and more data (or resource) rich gold-standard stock assessments. However, formally stock assessed fisheries represent a very biased subset of global fisheries, and it is entirely possible that a method that performs well for the kinds of species and fisheries that are commonly stock assessed might struggle in the kinds of fisheries that typically are unassessed.  --> -->

<!-- <!-- Alternatively though, while we may lack formal assessment for many regions of the world, stakeholders familiar with a region often have a general sense of the state of fisheries in a region. As outlined in Table.\@ref(tab:status-tab), while we often have no proof that results finding that for example fisheries in south-east Asia have similar stock status to those in Alaska, very few experts would agree that this is a plausible result XX tough statement to make in a paper xx. We use two case studies here to present the potential of additional, broadly applicable, data to potentially improve on "catch-only" methods.  --> -->

@@

>>>>

---
title: "Global Assessments of Fishery Status need Better Data more than Better Models"
author: 
  - Daniel Ovando
  - Ray Hilborn
  - Cole Monnahan
  - Merrill Rudd
  - Rishi Sharma
  - James Thorson
  - Yannick Rousseau
  - Yimin Ye
date: "`r Sys.Date()`"
bibliography: ["../references.bib"]
csl: nature.csl
output: 
  bookdown::word_document2:
    reference_docx: word-template.docx
  bookdown::pdf_document2: default
params:
  results_name: ["v0.5"]
  min_years_catch: [25]
abstract: |
  Assessments of the global state of fisheries play an important role in shaping the public narrative around ocean health, motivating future directions of research and funding, formulating evidence-based policy and tracking the implementation of the United Nations Sustainable Development Goals. Numerous high-profile publications featuring a range of statistical methods have produced estimates of the global status of fisheries, but limited quantity and quality of data along with methdological differences have produced counterintuitive and conflicting results and therefore, high uncertainties in our understanding of global fisheries. This is especially true in areas such as Southeast Asia and Africa which are also regions that have high dependence on fishery resources. How can we effectively estimate the state of global fishery sustainability and track progress towards the Sustainable Development Goals targets? We developed a new flexible assessment model to assess the value of different kinds, quantities, and quality of data in improving estimates of fishery stock status. We then explore avenues for obtaining potentially impactful data, including through the use of local expert opinion through Fisheries Management Index scores, and increasingly available but historically underutilized data such as trawl footprints and effort data. These data are then used to illustrate how different types of information paint starkly different pictures of the state of fisheries around the world, and to identify priority data types for future collection. We show that our ability to obtain reliable estimates of stock status for the world's unassessed fisheries depends on prioritizing the collection of key data at a global scale, not on the development of new modeling methods alone.
always_allow_html: true
---

@@

 <!-- Evaluating the validity of data-limited assessments methods can be challenging. Simulation testing provides one avenue, but it can be difficult to create a simulation environment that adequately captures the problems of real-world ecosystems and data. We can also compare results between data-limited assessment and more data (or resource) rich gold-standard stock assessments. However, formally stock assessed fisheries represent a very biased subset of global fisheries, and it is entirely possible that a method that performs well for the kinds of species and fisheries that are commonly stock assessed might struggle in the kinds of fisheries that typically are unassessed.  -->

 <!-- Alternatively though, while we may lack formal assessment for many regions of the world, stakeholders familiar with a region often have a general sense of the state of fisheries in a region. As outlined in Table.\@ref(tab:status-tab), while we often have no proof that results finding that for example fisheries in south-east Asia have similar stock status to those in Alaska, very few experts would agree that this is a plausible result XX tough statement to make in a paper xx. We use two case studies here to present the potential of additional, broadly applicable, data to potentially improve on "catch-only" methods.  -->

@@

```{}
